Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
Refine statement about the Galactic potential

Figure~\ref{fig:one_orbit_wrong_ref} shows that the actions computed in the
offset coordinate systems depend on the time (i.e. orbital phase) at which the
star's phase-space position is observed. (To our extremely long-lived observer
this would appear as time-dependence in the actions, which appear to oscillate
around their value using the correct coordinate system even though in this
example the Galaxy is described perfectly by a static, axisymmetric
potential.) The relative size of the phase variation in each action depends on
the direction of the systematic offset as well as the true values of the
actions (i.e. the type of orbit). In reality we will have one measurement of
the phase-space position to work with, in which case the determination of the
orbital phase in $z$ or $R$ is degenerate with the degree of systematic offset
in that coordinate (see Figure~\ref{fig:cartoon}). Additionally, in searching
for migrated members of known open clusters, we would compute actions for
stars with a wide range of orbital phases and locations in the Galaxy. In the
following we therefore quote percentile ranges for the possible values
computed for each action as a proxy for the effect of these systematic errors
in the coordinate system.

>>>>

Figure~\ref{fig:one_orbit_wrong_ref} shows that the actions computed in the
offset coordinate systems depend on the time (i.e. orbital phase) at which the
star's phase-space position is observed. To our extremely long-lived observer
this would appear as time-dependence in the actions, which appear to oscillate
around their value using the correct coordinate system even though in this
example the observer is using the correctly constructed best-fit static,
axisymmetric potential. The relative size of the phase variation in each
action depends on the direction of the systematic offset as well as the true
values of the actions (i.e. the type of orbit). In reality we will have one
measurement of the phase-space position to work with, in which case the
determination of the orbital phase in $z$ or $R$ is degenerate with the degree
of systematic offset in that coordinate (see Figure~\ref{fig:cartoon}).
Additionally, in searching for migrated members of known open clusters, we
would compute actions for stars with a wide range of orbital phases and
locations in the Galaxy. In the following we therefore quote percentile ranges
for the possible values computed for each action as a proxy for the effect of
these systematic errors in the coordinate system.
